---
title: "Our interactive report"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(palmerpenguins)
library(tidyverse) # data tidying and plots
library(ggridges) #fancy density plots
library(gridExtra) # stich together multiple charts
library(correlation) # correlation analysis
library(see) # correlation heatmap
library(plotly) # interactive data vis
library(shiny)
# setting data

## total data
df <- penguins %>% 
  select(-year ) %>% 
  mutate(sex = as.factor(str_to_title(sex))) %>%
  na.omit()

## for differences by sex
total_sex <- df %>% 
  select(sex, flipper_length_mm, body_mass_g , bill_length_mm ,bill_depth_mm ) 

### Here we use the `subset()` function to split our data
male <- total_sex %>% 
  subset(sex == "Male") 

female <- total_sex %>% 
  subset(sex == "Female") 

## for differences by species

total_species <-  df %>%  
  select(species, flipper_length_mm, body_mass_g , bill_length_mm ,bill_depth_mm ) 

### Using  `subset()` again, but this time by species
Adelie <- total_species %>%
  subset(species == "Adelie")

Chinstrap <- total_species %>%
  subset(species == "Chinstrap")

Gentoo <- total_species %>%
  subset(species == "Gentoo")

## Differences by Sex by Species

### This time we are using `subset()` to split by sex and by species
Male_Adelie <- df %>% subset(sex == "Male" & 
                       species == "Adelie")

Female_Adelie <- df %>% subset(sex == "Female" & 
                       species == "Adelie")

Male_Chinstrap <- df %>% subset(sex == "Male" & 
                       species == "Chinstrap")

Female_Chinstrap <- df %>% subset(sex == "Female" & 
                       species == "Chinstrap")

Male_Gentoo <- df %>% subset(sex == "Male" & 
                       species == "Gentoo")

Female_Gentoo <- df %>% subset(sex == "Female" &
                       species == "Gentoo") 
```




By Penguin Sex
===========================================================

Column {.sidebar}
-----------------------------------------------------------------------
```{r}
selectInput("v_sex", label = "Sex", choices = c("Female", "Male", "All"), 
            selected = "All")
```


Column {.tabset data-width=400}
-----------------------------------------------------------------------

### Density Histogram

```{r, echo = FALSE, message = FALSE}
renderPlot({
  df %>%
    select(-species, -island) %>% #removing island and species
    na.omit() %>%
    pivot_longer(-sex) %>%
    group_by(name) %>%
    mutate(value = scale(value)) %>%
    ungroup() %>%
    filter(str_detect(sex, if_else(input$v_sex == "All", "ale", input$v_sex))) %>%
    ggplot(aes(x=value, y = name, fill = I(ifelse(sex== "Female", "red", "blue")))) +
   # scale_color_identity() +
    geom_density_ridges(alpha = .7)+
    theme_classic() +
    theme(legend.position = "bottom") +
    labs(y= "")
})



```

### Boxplot 

```{r, echo = FALSE, message = FALSE}
renderPlot({
  df %>% 
    select(-species, -island) %>% #removing island and species
    na.omit() %>%
    pivot_longer(-sex) %>%
    group_by(name) %>%
    mutate(value = scale(value)) %>%
    ungroup()%>%
    filter(str_detect(sex, if_else(input$v_sex == "All", "ale", input$v_sex))) %>%
    ggplot(aes(y=value, x = name, fill = I(ifelse(sex== "Female", "red", "blue")))) +
    geom_boxplot(alpha = .7)+
    theme_classic() +
    theme(legend.position = "bottom") +
    labs(x ="")
})
```

### Scatter Charts

```{r}

renderPlot({
p1 <-df %>%
          filter(str_detect(sex, if_else(input$v_sex == "All", "ale", input$v_sex))) %>%
          ggplot(aes(x = flipper_length_mm, y = body_mass_g)) +
          geom_point(alpha = .7, size =2, aes(col = I(ifelse(sex== "Female", "red", "blue")))) +
          geom_smooth(method = "lm") +
          theme_classic() +
          theme(legend.position = "bottom")

p2 <- df %>%
          filter(str_detect(sex, if_else(input$v_sex == "All", "ale", input$v_sex))) %>%
          ggplot(aes(x = flipper_length_mm, y = bill_length_mm)) +
          geom_point(alpha = .7, size =2, aes(col = I(ifelse(sex== "Female", "red", "blue")))) +
          geom_smooth(method = "lm") +
          theme_classic() +
          theme(legend.position = "bottom")

p3 <- df %>%
  filter(str_detect(sex, if_else(input$v_sex == "All", "ale", input$v_sex))) %>%
    ggplot(aes(x = flipper_length_mm, y = bill_depth_mm)) +
    geom_point(alpha = .7, size =2, aes(col = I(ifelse(sex== "Female", "red", "blue")))) +
    geom_smooth(method = "lm") +
    theme_classic() +
    theme(legend.position = "bottom")


p4 <-  df %>%
    filter(str_detect(sex, if_else(input$v_sex == "All", "ale", input$v_sex))) %>%
    ggplot(aes( x = body_mass_g, y = bill_length_mm)) +
    geom_point(alpha = .7,  size =2, aes(col = I(ifelse(sex== "Female", "red", "blue")))) +
    geom_smooth(method = "lm") +
    theme_classic() +
    theme(legend.position = "bottom")


p5 <- df %>%
    filter(str_detect(sex, if_else(input$v_sex == "All", "ale", input$v_sex))) %>%
    ggplot(aes( x = body_mass_g, y = bill_depth_mm)) +
    geom_point(alpha = .7, size =2, aes(col = I(ifelse(sex== "Female", "red", "blue")))) +
    geom_smooth(method = "lm") +
    theme_classic() +
    theme(legend.position = "bottom")

p6 <- df %>%
    filter(str_detect(sex, if_else(input$v_sex == "All", "ale", input$v_sex))) %>%
    ggplot(aes( x = bill_length_mm, y = bill_depth_mm)) +
    geom_point(alpha = .7, size =2, aes(col = I(ifelse(sex== "Female", "red", "blue")))) +
    geom_smooth(method = "lm") +
    theme_classic() +
    theme(legend.position = "bottom")

grid.arrange(p1, p2, p3, p4, p5, p6)
})



```




Column {.tabset data-width=300}
-----------------------------------------------------------------------

### Total

```{r, echo = FALSE, message = FALSE}
results <- correlation(total_sex)
summary(results, redundant = TRUE) %>%
  plot() +
  theme(legend.position = "")
```

### Male

```{r, echo = FALSE, message = FALSE}
results <- correlation(male)
summary(results, redundant = TRUE) %>%
  plot() +
  theme(legend.position = "")
```

### Female

```{r, echo = FALSE, message = FALSE}
results <- correlation(female)
summary(results, redundant = TRUE) %>%
  plot() +
  theme(legend.position = "")
```


Differences by Species
===========================================================

Column {.sidebar}
-----------------------------------------------------------------------
```{r}
selectInput("v_species", label = "Species", choices = c("All", "Adelie", "Chinstrap", "Gentoo"), 
            selected = "All")
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Density Histogram

```{r, echo = FALSE, message = FALSE}
renderPlot({
  df %>%
    select(-sex, -island) %>% #removing island and species
    na.omit() %>%
    pivot_longer(-species) %>%
    group_by(name) %>%
    mutate(value = scale(value)) %>%
    ungroup() %>%
    filter(str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
    ggplot(aes(x=value, y = name, fill = I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
    geom_density_ridges(alpha = .7)+
    theme_classic() +
    theme(legend.position = "bottom") +
    labs(y= "")
})

```

### Boxplot 

```{r, echo = FALSE, message = FALSE}
renderPlot({
  df %>% 
    select(-sex, -island) %>% #removing island and species
    na.omit() %>%
    pivot_longer(-species) %>%
    group_by(name) %>%
    mutate(value = scale(value)) %>%
    ungroup()%>%
    filter(str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
    ggplot(aes(y=value, x = name, fill = I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
    geom_boxplot(alpha = .7)+
    theme_classic() +
    theme(legend.position = "bottom") +
    labs(x ="")
})
```

### Scatter Charts

```{r}

renderPlot({
p1 <-df %>%
          filter(str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
          ggplot(aes(x = flipper_length_mm, y = body_mass_g)) +
          geom_point(alpha = .7, size =2, aes(col = I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
          geom_smooth(method = "lm") +
          theme_classic() +
          theme(legend.position = "bottom")

p2 <- df %>%
          filter(str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
          ggplot(aes(x = flipper_length_mm, y = bill_length_mm)) +
          geom_point(alpha = .7, size =2, aes(col = I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
          geom_smooth(method = "lm") +
          theme_classic() +
          theme(legend.position = "bottom")

p3 <- df %>%
  filter(str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
    ggplot(aes(x = flipper_length_mm, y = bill_depth_mm)) +
    geom_point(alpha = .7, size =2, aes(col =  I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
    geom_smooth(method = "lm") +
    theme_classic() +
    theme(legend.position = "bottom")


p4 <-  df %>%
    filter(str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
    ggplot(aes( x = body_mass_g, y = bill_length_mm)) +
    geom_point(alpha = .7, size =2, aes(col =  I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
    geom_smooth(method = "lm") +
    theme_classic() +
    theme(legend.position = "bottom")


p5 <- df %>%
    filter(str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
    ggplot(aes( x = body_mass_g, y = bill_depth_mm)) +
    geom_point(alpha = .7, size =2, aes(col =  I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
    geom_smooth(method = "lm") +
    theme_classic() +
    theme(legend.position = "bottom")

p6 <- df %>%
    filter(str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
    ggplot(aes( x = bill_length_mm, y = bill_depth_mm)) +
    geom_point(alpha = .7, size =2, aes(col =  I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
    geom_smooth(method = "lm") +
    theme_classic() +
    theme(legend.position = "bottom")

grid.arrange(p1, p2, p3, p4, p5, p6)
})



```




Column {.tabset data-width=300}
-----------------------------------------------------------------------

### Total

```{r, echo = FALSE, message = FALSE}
results <- correlation(total_species)
summary(results, redundant = TRUE) %>%
  plot() +
  theme(legend.position = "")
```

### Adelie

```{r, echo = FALSE, message = FALSE}
results <- correlation(Adelie)
summary(results, redundant = TRUE) %>%
  plot() +
  theme(legend.position = "")
```

### Chinstrap
```{r, echo = FALSE, message = FALSE}
results <- correlation(Chinstrap)
summary(results, redundant = TRUE) %>%
  plot() +
  theme(legend.position = "")
```

### Gentoo

```{r, echo = FALSE, message = FALSE}
results <- correlation(Gentoo)
summary(results, redundant = TRUE) %>%
  plot() +
  theme(legend.position = "")
```

Differences between Sex between each Species
===========================================================


Column {.sidebar}
-----------------------------------------------------------------------
```{r}

selectInput("v_sex", label = "Sex", choices = c("Female", "Male", "All"), 
             selected = "All")

selectInput("v_species", label = "Species", choices = c("All", "Adelie", "Chinstrap", "Gentoo"), 
            selected = "All")

```

Column {.tabset data-width=500}
-----------------------------------------------------------------------
### Density Histogram

```{r, echo = FALSE, message = FALSE}
renderPlot({
  df %>%
    select( -island) %>% #removing island and species
    na.omit() %>%
    filter(str_detect(sex, if_else(input$v_sex == "All", "ale", input$v_sex)) &
           str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
    pivot_longer(c(-sex,-species) ) %>%
    group_by(name) %>%
    mutate(value = scale(value)) %>%
    ungroup() %>%
    ggplot(aes(x=value, y = name, fill = I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
    facet_wrap(~sex) +
    geom_density_ridges(alpha = .7)+
    theme_classic() +
    theme(legend.position = "bottom") +
    labs(y= "")
})

    
    
```

### Boxplot 

```{r, echo = FALSE, message = FALSE}
renderPlot({
  df %>% 
    select( -island) %>% #removing island and species
    na.omit() %>%
    filter(str_detect(sex, if_else(input$v_sex == "All", "ale", input$v_sex)) &
           str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
    pivot_longer(c(-sex,-species) ) %>%
    group_by(name) %>%
    mutate(value = scale(value)) %>%
    ungroup()%>%
    ggplot(aes(y=value, x = name, fill = I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
    facet_wrap(~sex) +
    geom_boxplot(alpha = .7)+
    theme_classic() +
    theme(legend.position = "bottom") +
    labs(x ="")
})
```

### Scatter Charts

```{r}

renderPlot({
p1 <-df %>%
          filter(str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
          ggplot(aes(x = flipper_length_mm, y = body_mass_g)) +
          facet_wrap(~sex) +
          geom_point(alpha = .7, size =2, aes(col = I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
          geom_smooth(method = "lm") +
          theme_classic() +
          theme(legend.position = "bottom")

p2 <- df %>%
          filter(str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
          ggplot(aes(x = flipper_length_mm, y = bill_length_mm)) +
          facet_wrap(~sex) +
          geom_point(alpha = .7, size =2, aes(col = I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
          geom_smooth(method = "lm") +
          theme_classic() +
          theme(legend.position = "bottom")

p3 <- df %>%
  filter(str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
    ggplot(aes(x = flipper_length_mm, y = bill_depth_mm)) +
    facet_wrap(~sex) +
    geom_point(alpha = .7, size =2, aes(col =  I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
    geom_smooth(method = "lm") +
    theme_classic() +
    theme(legend.position = "bottom")


p4 <-  df %>%
    filter(str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
    ggplot(aes( x = body_mass_g, y = bill_length_mm)) +
    facet_wrap(~sex) +
    geom_point(alpha = .7, size =2, aes(col = I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
    geom_smooth(method = "lm") +
    theme_classic() +
    theme(legend.position = "bottom")


p5 <- df %>%
    filter(str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
    ggplot(aes( x = body_mass_g, y = bill_depth_mm)) +
    facet_wrap(~sex) +
    geom_point(alpha = .7, size =2, aes(col = I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
    geom_smooth(method = "lm") +
    theme_classic() +
    theme(legend.position = "bottom")

p6 <- df %>%
    filter(str_detect(species, if_else(input$v_species == "All", "[ea]", input$v_species))) %>%
    ggplot(aes( x = bill_length_mm,  y = bill_depth_mm)) +
    facet_wrap(~sex) +
    geom_point(alpha = .7, size =2, aes(col =  I(case_when(
      species == "Adelie" ~ "purple1",
      species == "Chinstrap" ~ "green4",
      species == "Gentoo" ~ "orange"
      )))) +
    geom_smooth(method = "lm") +
    theme_classic() +
    theme(legend.position = "bottom")

grid.arrange(p1, p2, p3, p4, p5, p6)
})



```

Column {.tabset data-width=300}
-----------------------------------------------------------------------

### Total

#### Male

```{r, echo = FALSE, message = FALSE}
results <- correlation(male)
summary(results, redundant = TRUE) %>%
  plot() +
    theme(legend.position = "")
```

#### Female

```{r, echo = FALSE, message = FALSE}
results <- correlation(female)
summary(results, redundant = TRUE) %>%
  plot() +
    theme(legend.position = "")
```

### Adelie 

#### Male
```{r, echo = FALSE, message = FALSE}
results <- correlation(Male_Adelie)
summary(results, redundant = TRUE) %>%
  plot()+
    theme(legend.position = "")
```

#### Female
```{r, echo = FALSE, message = FALSE}
results <- correlation(Female_Adelie)
summary(results, redundant = TRUE) %>%
  plot() +
    theme(legend.position = "")
```

### Chinstrap 

#### Male 
```{r, echo = FALSE, message = FALSE}
results <- correlation(Male_Chinstrap)
summary(results, redundant = TRUE) %>%
  plot() +
    theme(legend.position = "")
```

#### Female 

```{r, echo = FALSE, message = FALSE}
results <- correlation(Female_Chinstrap)
summary(results, redundant = TRUE) %>%
  plot() +
    theme(legend.position = "")
```

### Gentoo 

#### Male 
```{r, echo = FALSE, message = FALSE}
results <- correlation(Male_Gentoo)
summary(results, redundant = TRUE) %>%
  plot() +
    theme(legend.position = "")
```

#### Female 
```{r, echo = FALSE, message = FALSE}
results <- correlation(Female_Gentoo)
summary(results, redundant = TRUE) %>%
  plot() +
    theme(legend.position = "")
```
